%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{red}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Musa V.}{Ahmed}
\title{Cover Letter}                               % optional, remove / comment the line if not wanted
\address{20197 NW 10th Street}{Pembroke Pines, FL 33029}{USA}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{+1~(954)~993~0768}                   % optional, remove / comment the line if not wanted
%\phone[fixed]{+2~(345)~678~901}                    % optional, remove / comment the line if not wanted
%\phone[fax]{+3~(456)~789~012}                      % optional, remove / comment the line if not wanted
\email{mahme012@fiu.edu}                               % optional, remove / comment the line if not wanted
\homepage{/in/musavahmed}                         % optional, remove / comment the line if not wanted
%\extrainfo{additional information}                 % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Through passion I gain strength}                                 % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%-----       letter       ---------------------------------------------------------
% recipient data
\recipient{Dr. Jamie Foster}{University of Florida\\Department of Microbiology and Cell Science\\}
\date{April 8, 2015}
\opening{Dr. Foster:}
\closing{Regards,}
\enclosure[Attached]{curriculum vit\ae{}}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
\makelettertitle

I am currently a graduate student at Florida International University pursuing a Master's
Degree in Computer Science. I posses a strong background in computer networking simulation and
modeling as well as high performance distributed computing. As part of my coursework, research,
and thesis I must be in a constant state of problem solving. This includes but is not limited
to software design, objected-oriented programming, imperative programming, data analysis, automation with
scripting, software testing, reading and adapting novel ideas from major publications, and
constant tinkering for optimizations or stress testing. I feel my
experience makes me the ideal candidate for this position.

I have been programming and messing around with the computer since I was three. My father is a
Computer Scientist by trade and he introduced me to computers at young age. By the time I was
ten years old I had already rejected Windows and preferred to use Linux on all of my
computers.

When I came to college my side interest in Linux, experimentation, open source software, and programming
turned into something palpable that I could use and apply in the real world. I excelled in all
my courses and worked hard. Eventually I was accepted into the highly prestigious 4+1 accelerated
Bachelors and Masters program. 

Not far into my undergraduate career I was accepted to conduct undergraduate research. I firmly believe 
this is where my skills and knowledge of Linux and programming set me apart from the other
students. The research was challenging and their were several topics of which I was completely
uneducated about. However, I rose to challenge and I found that I genuienly enjoyed it. After seeing 
my committment and dedication to the work, my advisor agreed to take me on for Master's thesis, 
a rare event in my department. In over four years at the university I have only seen one other 
Master's student defend a thesis in Computer Science.

Recently, I have been working on my thesis which consists of hybrid approach to network
simulation and emulation. Part of this project required extensive data collection on each
computer to see what kind of data is it transmitting and how much, this can be thought of as
network metadata. This data is then filtered, analyzed, and finally sent to a discrete-event 
simulator for processing. The entire data collection part was written in a combination of 
Python and Bash scripts (mainly for automation and some small speed optimizations).

I firmly believe I can be a serious asset to your project. The field of metagenomics is
extremely interesting to me as there is a massive amount of data integration and analysis. The
possibilities for statistical analysis and modeling are endless. Let me further describe my
experience and skills particular those relating to data analysis. Again, as part of my research
I must taken


\end{document}


%% end of file `template.tex'.
