%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.0 (5/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing

\addbibresource{bibliography.bib} % Specify the bibliography file to include publications

\begin{document}

\header{Musa V.}{ Ahmed}{graduate research assistant} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{Contact}
20197 NW 10th ST
Pembroke Pines, FL 33029 
USA
~
(954) 993 0768 
~
mahme012@fiu.edu
/in/musavahmed
\section{languages}
English
Urdu, Hindi \& Punjabi 
\section{Programming}
{\color{red} $\varheartsuit$} Java
Python \& C++ 
\section{Skills}
Object-oriented
Imperative
Testing, Scripting
LaTeX, Linux 
Emulation \& Simulation
\end{aside}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\begin{entrylist}
%------------------------------------------------
\entry
{2014--2015}
{Masters {\normalfont of Computer Science}}
{Florida International University}
{\emph{In Progress} \\
Cumulative GPA: 3.5}
%------------------------------------------------
\entry
{2012--2014}
{Bachelor {\normalfont of Computer Science}}
{Florida International University}
{Cumulative GPA: 3.45}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Experience}

\begin{entrylist}
%------------------------------------------------
\entry
{2014--Now}
{Florida International University}
{Miami, Florida}
{\emph{Graduate Research Assistant} \\
Developed spreadsheets for risk analysis on exotic derivatives on a wide array of commodities (ags, oils, precious and base metals), managed blotter and secondary trades on structured notes, liaised with Middle Office, Sales and Structuring for bookkeeping. \\
Detailed achievements:
\begin{itemize}
\item Learned how to make amazing coffee
\item Finally determined the reason for \textsc{PC LOAD LETTER}:
\begin{itemize}
\item Paper jam
\item Software issues:
\begin{itemize}
\item Word not sending the correct data to printer
\item Windows trying to print in letter format
\end{itemize}
\item Coffee spilled inside printer
\end{itemize}
\item Broke the office record for number of kitten pictures in cubicle
\end{itemize}}
%------------------------------------------------
\entry
{2014}
{Florida International University}
{Miami, Florida}
{\emph{Undergraduate Research Assistant} \\
Rated "truly distinctive" for Analytical Skills and Teamwork.}
%------------------------------------------------
\entry
{2013}
{Florida International University}
{Miami, Florida}
{\emph{Teaching Assistant} \\
Worked in the Nerd Herd and helped to solve computer problems by asking customers to turn their computers off and on again.}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{Awards}
\begin{entrylist}
%------------------------------------------------
\entry
{2014}
{Outstanding Undergraduate Student}
{Florida International University}
{Finalist among top students in their final year of a Bachelors degree.}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	COMMUNICATION SKILLS SECTION
%----------------------------------------------------------------------------------------
\clearpage
\section{Communication Skills}
\begin{entrylist}
%------------------------------------------------
\entry
{2014}
{Oral Presentation}
{Florida International University}
{As part of the course work for CIS4911, I presented my work for senior thesis.}
%------------------------------------------------
\entry
{2014}
{Oral Presenation}
{GEC 21, Indiana University}
{For GEC 21, I presented my work on the demo floor.}
%------------------------------------------------
\entry
{2013}
{Poster}
{Florida International University}
{For GEC 21, I created a poster which demonstrates the features of MyExperiment.}
%------------------------------------------------
\entry
{2013}
{Poster}
{Florida International University}
{As part of the course work for CIS4911, I created a poster which demonstrates my senior thesis.}
%------------------------------------------------
\entry
{2013}
{Poster}
{Florida International University}
{As part of the course work for CGS3095, I created a poster that shows the rapid advent of unmanned aerial vehicles.}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{Interests}

\textbf{professional:} data analysis, company profiling, risk analysis, economics, web design,
web app creation, software design, marketing \\
\textbf{personal:} piano, chess, cooking, dancing, running

%----------------------------------------------------------------------------------------
%	COURSE WORK SECTION
%----------------------------------------------------------------------------------------

\section{Course Work}

\paragraph{Computer Science}
\paragraph{Mathematics}

%----------------------------------------------------------------------------------------

\end{document}
